% TEMPLATE for Usenix papers, specifically to meet requirements of
%  USENIX '05
% originally a template for producing IEEE-format articles using LaTeX.
%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
% adapted by David Beazley for his excellent SWIG paper in Proceedings,
%   Tcl 96
% turned into a smartass generic template by De Clarke, with thanks to
%   both the above pioneers
% use at your own risk.  Complaints to /dev/null.
% make it two column with no page numbering, default is 10 point

% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
% the .sty file from the LaTeX source template, so that people can
% more easily include the .sty file into an existing document.  Also
% changed to more closely follow the style guidelines as represented
% by the Word sample file. 

% Note that since 2010, USENIX does not require endnotes. If you want
% foot of page notes, don't include the endnotes package in the 
% usepackage command, below.

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage{graphicx}
\usepackage{url}
\usepackage{listings}
%\usepackage{subfigure}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{paralist}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{algpseudocode}
\usepackage{algorithm}

\input{commands}

\newcommand{\comment}[1]{}

\begin{document}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Countermeasures Against Active Routing Attacks on Tor}
\author{Yes, we need a more exciting title. Maybe giving it a nice name?}

%for single author (just remove % characters)
%\author{
%{}\\
%Princeton University
%\and
%{}\\
%Princeton University
%\and
%{}\\
%Princeton University
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
%} % end author

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}

\subsection*{Abstract}
Anonymity systems such as Tor are known to be vulnerable to network-level adversaries who can observe both ends of the communication to deanonymize Tor users. Recent works have shown that Tor is susceptible to the previously unknown active BGP routing attacks, which expose Tor users to more potential network-level adversaries. This paper aims at mitigating and detecting such active routing attacks against Tor. We first present a new measurement study on the resilience of the Tor network to active BGP prefix attacks. We show that Autonomous Systems which carry a large portion of Tor traffic, such as OVH, only have relatively low resilience to active attacks. Next, we present a novel guard relay selection algorithm which incorporates resilience of relays into considerations. We show that the new algorithm successfully lowers the probability of a Tor client being affected by an attack by 35\%, and at the same time provides better anonymity to the Tor client. Finally, the paper demonstrates a live monitoring framework that can detect routing anomaly on the Tor network in real time. 

%We also present a set of novel countermeasures that will help 
%prevent these types of attacks from being successful: a new path selection algorithm, 
%a live monitoring framework that uses a variety of heuristics for attack detection, and 
%suggestions for Tor relay operators. 

\input{intro}
\input{background}
\input{measure}
\input{proactive}
\input{reactive}
\input{discussion}
%\input{related}
%\input{future}
\input{conclusion}

{\footnotesize \bibliographystyle{acm}
\bibliography{sigproc.bib}}

%\theendnotes

\end{document}







